Demonstration of Effect of Indexing on\\ Cobb-Douglas and CES\\ Aggregate Production Functions

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Minor changes.

The CES model with raw historical data is given by
%
\begin{equation} \label{eq:CESkl_nonindexed}
  Y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta K^{-\rho}
      + (1-\delta)L^{-\rho} \right]^{-1/\rho} \; .
\end{equation}

@@

The Cobb-Douglas model indexed historical data is given by
%
\begin{equation} \label{eq:CD_model}
  y = \theta \: \mathrm{e}^{\lambda t} \: k^{\alpha_k} \, l^{\alpha_l} \; ,
\end{equation}
%
where $y$, $k$, and $l$ are indexed by ratio to the initial year (1960). 
For example,
%
\begin{equation} \label{eq:indexing}
  y = Y/Y_{1960} \; .
\end{equation}

@@

All data are from the Penn World Table.
Figure~\ref{fig:GDP-graph} below shows historical data as dots.

@@

Next, we fit both the Cobb-Douglas and CES aggregate production functions 
to both indexed and non-indexed data.
Figure~\ref{fig:GDP-graph} below shows historical data as lines.

@@

We graph each type of fitted model against historical data.
Note that all models provide excellent fits.

@@

Here are the coefficients for the Cobb-Douglas models.
<<cd-coeffs>>=
cd_nonindexed
cd_indexed
@

Note that the fitted parameters 
output elasticity
\verb+alpha_1+ ($\alpha_k$) 
and 
Solow residual growth rate
\verb+lambda+
are identical,
regardless of whether the historical data are indexed or not.

@@

Note that $\theta$ for the indexed model is near 1.0, as expected.

@@

The following shows parameters for CES models
fitted to non-indexed and indexed historical data.

@@

As expected, and similar to the Cobb-Douglas model,
the growth rate of the Solow residual
(\verb+gamma+)
is identical, regardless of whether the historical data are indexed or not.
Again, similar to the Cobb-Douglas model, 
the pre-multiplier term
(in this case \verb+gamma+)
is different depending upon whether the historical data were indexed or not.
We note that the value of \verb+gamma+ is close to 1,
when fitting to indexed data,
as expected.
Furthermore, the elasticity of substitution parameters
(\verb+rho+)
are identical regardless of whether the historical data are indexed or not.

>>>>

The CES model with raw historical data is given by
%
\begin{equation} \label{eq:CESkl_nonindexed}
  Y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta K^{-\rho}
      + (1-\delta)L^{-\rho} \right]^{-1/\rho} \; ,
\end{equation}
%
where $\rho$ is related to the elasticity of substitution~($\sigma$) by 
%
\begin{equation} \label{eq:sigma}
  \sigma = \frac{1}{1 + \rho} \; .
\end{equation}

@@

The Cobb-Douglas model with indexed historical data is given by
%
\begin{equation} \label{eq:CD_model}
  y = \theta \: \mathrm{e}^{\lambda t} \: k^{\alpha_k} \, l^{\alpha_l} \; ,
\end{equation}
%
where $y$, $k$, and $l$ are indexed by ratio to the initial year (1960). 
For example,
%
\begin{equation} \label{eq:indexing}
  y = Y/Y_{1960} \; .
\end{equation}

@@

All historical data are from the Penn World Table.
Figure~\ref{fig:GDP-graph} below shows historical data as dots.

@@

We fit both the Cobb-Douglas and CES aggregate production functions 
to both raw and indexed data.
Figure~\ref{fig:GDP-graph} below shows fitted GDP as lines.

@@

Figure~\ref{fig:GDP-graph} compares each type of fitted model (lines) with historical data (dots).
Note that all models provide excellent fits.

@@

The coefficients for Cobb-Douglas models are shown below.
<<cd-coeffs>>=
cd_nonindexed
cd_indexed
@

Note that output elasticity
\verb+alpha_1+ ($\alpha_k$) 
and 
Solow residual growth rate
\verb+lambda+
are identical,
regardless of whether the historical data are indexed or raw.

@@

Note that $\theta$ for the model fit to indexed data is near 1.0, as expected.

@@

The following shows parameters for CES models
fitted to raw and indexed historical data.

@@

Similar to the Cobb-Douglas model,
the pre-multiplier term
(in this case \verb+gamma+)
is different depending upon whether the historical data were indexed or raw.
As expected, and similar to the Cobb-Douglas model,
the growth rate of the Solow residual
(\verb+gamma+)
is identical, regardless of whether the historical data are indexed or raw.
We note that the value of \verb+gamma+ is close to 1.0,
when fitting to indexed data,
as expected.
Furthermore, the elasticity of substitution exponents
(\verb+rho+)
are identical regardless of whether the historical data are indexed or not.
